Verifying Demonstrations

### 2018-11-29 paper/adversary-model.tex

We now provide a concretely defined system and adversary model.
We give three definitions, each defines an adversary with increasingly stronger 
capabilities (\ie more auxiliary information).

@@

\Cref{deanonymizing-storage-adversary} is a stronger adversary who also can 
observe the channel between \(P\) and \(S\).
\Eg a national state can potentially monitor the traffic of all \acp{ISP} and 
thus perform time-correlation attacks on messages on the network and events 
observed from \(S\).
We capture this in \cref{deanonymizing-storage-adversary}, where \(S\) learns 
the identity of \(P\).

>>>>

We now provide a concretely defined system and adversary model.
We give three definitions, each defining an adversary with increasingly stronger 
capabilities (\ie more auxiliary information).

@@

\Cref{deanonymizing-storage-adversary} is a stronger adversary.
Although the adversary cannot observe the channel between \(P\) and \(S\), the 
adversary can still learn the identity of \(P\).
\Eg a national state can potentially monitor the traffic of all \acp{ISP} and 
thus perform time-correlation attacks on messages on the network and events 
observed from \(S\).
We capture this in \cref{deanonymizing-storage-adversary}, where \(A\) learns 
the identity of \(P\) in the communication with \(S\).

### 2018-11-29 paper/location-proofs.tex

Some location-based services only grant access to resources to users located at a particular location, thus raising the issue of verifying the position claimed by a particular user. 
In most of the existing schemes, the location of a user/device is determined by the device itself (\eg through GPS) and forwarded to the location-based service provider. 
One of the main drawbacks of this approach is that a user can cheat by having her device transmit a false location. 
Therefore, it is possible for a user to be inappropriately granted access to a particular resource while being thousands of kilometers away.

One possible way to counter this threat is by having the requesting device formally prove that it really is at the claimed location, which gives rise to the concept of \emph{location proof}. 
In a nutshell, a location proof is a digital certificate attesting that someone was at a particular location at a specific moment in time. 
A location proof system is an architecture by which users can obtain location proofs from neighboring witnesses (\eg trusted access points or other users) that can later be shown to verifiers who can check the validity of a particular proof \cite{luo2010veriplace, zhu2011applaus}.
Most of the existing approaches to location proofs require the prover and the witnesses to disclose their identities, thus raising many privacy issues such as the possibility of tracing the movements of users of the location proof architecture.
However, some location proofs systems, such as PROPS~\cite{PROPS}, exist that provide strong privacy guarantees along with the possibility of verifying the claim of the location. \PRIVO shares some similarities with PROPS, although their objective is quite different as it aims at verifying a global property of the population (\ie crowd estimation) in contrast to checking the location claim made by a user, which is an individual property.

>>>>

Some location-based services only grant access to resources to users located at a particular location, thus raising the issue of verifying the position claimed by a particular user. 
In most of the existing schemes, the location of a user (or their device) is determined by the device itself (\eg through GPS) and forwarded to the location-based service provider. 
One of the main drawbacks of this approach is that a user can cheat by having their device transmit a false location. 
Therefore, it is possible for a user to be inappropriately granted access to a particular resource while being thousands of kilometers away.

One possible way to counter this threat is by having the requesting device formally prove that it really is at the claimed location, which gives rise to the concept of \emph{location proof}. 
In a nutshell, a location proof is a digital certificate attesting that someone was at a particular location at a specific moment in time. 
A location proof system is an architecture by which users can obtain location proofs from neighboring witnesses (\eg trusted access points or other users) that can later be shown to verifiers who can check the validity of a particular proof \cite{luo2010veriplace, zhu2011applaus}.
Most of the existing approaches to location proofs require the prover and the witnesses to disclose their identities, thus raising many privacy issues such as the possibility of tracing the movements of users of the location-proof architecture.
However, some location proofs systems, such as PROPS~\cite{PROPS}, exist that provide strong privacy guarantees along with the possibility of verifying the claim of the location.
\CROCUS shares some similarities with PROPS, although their objective is quite different as it aims at verifying a global property of the population (\ie crowd estimation) in contrast to checking the location claim made by a user, which is an individual property.
\sonja{any more differences to ours, relevance of this one?}
\simon{Yeah, there is a problem here. As it currently reads, I see no reason to not use PROPS directly as a building block for CROCUS, instead of devising our own distance-bounding. Maybe there is no authentication, it's ONLY a proof of location? I don't know, but some detail is missing.}

\sonja{add something on platin.io, details unknown but roughly relying on witnesses and graph theory (unique big cluster, assumption of honest majority)}

### 2018-11-29 paper/related-work.tex
Renames RelatedWork to related-work
Renames LocationProofs to location-proofs
coincoin

\section{Related work}%
\label{RelatedWork}

In this section, we first describe the crowd counting methods that are classically used to estimate the size of a crowd during a protest before reviewing the related work on location proof systems from which our solution \PRIVO is inspired.

@@

The seemingly most commonly used method for counting crowds at protests is \emph{Jacobs's method}~\cite{2016DemonstrationsInSeoul,BBCHowToCountProtestNumbers,HowWillWeKnowTrumpInauguralCrowdSize,TheXManMarch,TheCrowdNumbersGame}.
This manual method devised in the 1960s relies on aerial pictures of the event.
The verifier divides the protest venue into regions and then estimates the density of the crowd in the different regions before summing them up to get an estimate of the global count.
Clearly, this method is prone to errors as it is based on estimates.
It provides universal verifiability (\cref{UniversalVerif}) since anyone can redo the counting using the same pictures.
However, it is difficult to achieve individual verifiability (\cref{IndividualVerif}) using this method since it is hard to verify that oneself is indeed in any of the photos\footnote{It is of course possible with very detailed photos, but not currently realistic to do with aerial pictures.}.
We can argue that it also achieves eligibility (\cref{EligibilityVerif}) if all the photos are taken at the same point in time with no overlap, since then no one can be counted twice.
Unfortunately, we can only get the peak participation with this method.
When it comes to spatial and temporal eligibility, we have to rely on pictures (\eg by determining from the pictures themselves when and where the they were taken).
However, this is prone to cheating --- and subject to a variety of manipulation techniques --- and the best we can do is to employ forensic methods to try to detect any modifications or other attempts of fraud.
From a privacy perspective, all techniques based on photo or video material are necessarily not privacy-preserving unless the protesters take actions to protect themselves.
For instance, there is a risk that participants are recognizable from the material if they do not wear masks.

@@

In the computer vision community, there is a body of work on estimating the number of persons in a picture (\eg the work of \citet{NNCrowdCounting}).
This class of methods requires pictures or video surveillance of the protest location during the entire protest and are thus highly privacy-invasive.
They are generally based on machine learning techniques, and thus also require a training dataset to work.
In the work by \cite{NNCrowdCounting}, they actually train and evaluate their algorithm on different scenes, which might make this method easier to use for protesting.
Universal verifiability (\cref{UniversalVerif}) can be provided with this method, since someone can always recount the participants using the recorded video material.
Some degree of individual verifiability could also be provided (\cref{IndividualVerif}), if Alice can recognize her own face in the video, but still this might be difficult. 
Remark also that while automatic face recognition can help verifiability, it has a high impact on privacy.
In addition, it is difficult (if not impossible) to avoid to count some people twice, thus we cannot argue for eligibility (\cref{EligibilityVerif}).
In theory, this class of methods will provide an upper bound, whereas our method outputs a lower bound.
Furthermore, it is also difficult to capture the entire location on video surveillance, which diminishes the argument for an upper bound in practice.
The spatial and temporal verifiability properties are reduced to those of the video, which should be similar as in our discussion about the verifiability of photos (\ie, using forensic methods).

@@

During the protests in Seoul~\cite{2016DemonstrationsInSeoul}, one physical analytics company tried to estimate the number of participants using their physical analytics technology.
In a nutshell, this technology scans the MAC addresses emitted from the participants' smartphones during Wi-Fi probe requests.
However, in order to work this method makes many additional assumptions:
\blockcquote{2016DemonstrationsInSeoul}{%
The company presumed that about half of smartphone users usually leave on their Wi-Fi feature on and the other half switch it off, based on a separate survey on smartphone usage. 
It also assumed that about 20\% of the smartphone signals were repetition from the same device.
}
This method cannot provide any verifiability, as we must trust the company on performing the measurements correctly and to be honest about when and where they conducted them.
In addition, as MAC address randomization is now getting a wider adoption precisely to fight physical tracking, this method will not work any more, although some tracking of smartphones could still be possible~\cite{WhyMACRandomizationIsNotEnough}.

@@

One of the most closely related work to our scheme is \citet{CrowdCount}, which is a web service that lets Alice create an event such that anyone can submit his location to register that he is in Alice's event.
This method has the benefit of counting everyone who has declared his presence, not just the count at the snapshot of the pictures.
However, there is no verification as the service must be trusted to behave honestly, but even then, nothing prevents Bob from submitting more than once (violating eligibility, \cref{EligibilityVerif}).
Another downside is that the service also requires an Internet connection during the event to register as a participant.
This makes it prone to some form of denial-of-service attack.
For instance, if Alice has organized a protest against Grace's regime, who shuts down the cellular network or Internet backbone as a means to censor the protest.

Another related approach based on devices is UrbanCount~\cite{UrbanCount}, which relies on epidemic spreading of crowd-size estimates by device-to-device communication to count crowds in dense urban environments with high node-mobility and churn.
However, there is no consideration of a potentially adversarial setting and thus no verification or checks on eligibility.  DiVote~\cite{DiVote}, a prior work by the same authors for polling in dense areas, avoids double counting, but again only works with honest participants.

\input{LocationProofs.tex}

>>>>

\section{Related work}%
\label{related-work}

@@

The seemingly most common method for counting crowds at protests is \emph{Jacobs's method}~\cite{2016DemonstrationsInSeoul,BBCHowToCountProtestNumbers,HowWillWeKnowTrumpInauguralCrowdSize,TheXManMarch,TheCrowdNumbersGame}.
This manual method devised in the 1960s relies on aerial pictures of the event.
The verifier divides the protest venue into regions and then estimates the density of the crowd in the different regions before summing them up to get an estimate of the global count.
Clearly, this method is prone to errors as it is based on estimates.
It provides universal verifiability since anyone can redo the counting using the same pictures.
However, it is difficult to achieve individual verifiability using this method since it is hard to verify that oneself is indeed in any of the photos\footnote{It is of course possible with very detailed photos, but not currently realistic to do with aerial pictures.}.
We can argue that it also achieves eligibility if all the photos are taken at the same point in time, since then no one can be counted twice.
Unfortunately, we can only get the peak participation with this method.
When it comes to spatial and temporal eligibility, we have to rely on pictures (\eg by determining from the pictures themselves when and where they were taken).
However, this is prone to cheating --- and subject to a variety of manipulation techniques --- and the best we can do is to employ forensic methods to try to detect any modifications or other attempts of fraud.
From a privacy perspective, all techniques based on photo or video material are necessarily not privacy-preserving unless the protesters take actions to protect themselves.
For instance, there is a risk that participants are recognizable from the material if they do not wear masks.

@@

In the computer vision community, there is a body of work on estimating the number of persons in a picture (\eg the work of \cite{NNCrowdCounting}).
This class of methods requires pictures or video surveillance of the protest location during the entire protest and are thus highly privacy-invasive.
They are generally based on machine learning techniques, and thus also require a training dataset to work.
In the work by \cite{NNCrowdCounting}, they actually train and evaluate their algorithm on different scenes, which might make this method easier to use for protesting.
Universal verifiability can be provided with this method, since someone can always recount the participants using the recorded video material.
Some degree of individual verifiability could also be provided,
if Alice can recognize her own face in the video, but this might still be difficult. 
Remark also that while automatic face recognition can help verifiability, it has a high impact on privacy.
In addition, it is difficult (if not impossible) to avoid counting some people twice, thus we cannot argue for eligibility.
In theory, this class of methods will provide an upper bound
%, whereas our method outputs a lower bound
.
Furthermore, it is also difficult to capture the entire location on video surveillance, which diminishes the argument for an upper bound in practice.
The spatial and temporal verifiability properties are reduced to those of the video, which should be similar as in our discussion about the verifiability of photos (\ie, using forensic methods).

@@

During the protests in Seoul~\cite{2016DemonstrationsInSeoul}, one physical analytics company tried to estimate the number of participants using their physical analytics technology.
In a nutshell, this technology scans the MAC addresses emitted from the participants' smartphones during Wi-Fi probe requests.
However, in order to work this method makes many additional assumptions:
\blockcquote{2016DemonstrationsInSeoul}{%
The company presumed that about half of smartphone users usually leave on their Wi-Fi feature on and the other half switch it off, based on a separate survey on smartphone usage. 
It also assumed that about 20\% of the smartphone signals were repetition from the same device.
}
This method cannot provide any verifiability, as we must trust the company on performing the measurements correctly and to be honest about when and where they conducted them.
In addition, as MAC address randomization is now getting a wider adoption precisely to fight against physical tracking, this method will not work any more, although some tracking of smartphones could still be possible with a different method~\cite{WhyMACRandomizationIsNotEnough}.

@@

One of the works most closely related to our goal is \citet{CrowdCount}, which is a web service that lets Alice create an event such that anyone can submit their location to register that they are in Alice's event.
This method has the benefit of counting everyone who has declared their presence, not just the count at the snapshot of the pictures.
However, there is no verification as the service must be trusted to behave honestly, and even then, nothing prevents Bob from submitting more than once (violating eligibility).
Another downside is that the service also requires an Internet connection during the event to register as a participant.
This makes it prone to some form of denial-of-service attack.
For instance, if Alice has organized a protest against Grace's regime, Grace can shut down the cellular network or Internet backbone as a mean to censor the protest.

Another related approach based on devices is UrbanCount~\cite{UrbanCount}, which relies on epidemic spreading of crowd-size estimates by device-to-device communication to count crowds in dense urban environments with high node-mobility and churn.
However, there is no consideration of a potentially adversarial setting and thus no verifiability or checks on eligibility.  DiVote~\cite{DiVote}, a prior work by the same authors for polling in dense areas, avoids double counting, but again only works with honest participants.

\input{location-proofs.tex}
